Combining predicate transformer semantics for effects

### 2020-10-08 msfp2020/msfp2020.tex
Final version

In this work, we use a free monad to model effectful programs:

@@

\pause
The generic fold that computes a predicate of type \Set:
\begin{minted}{Agda}
[[_]] : Free C R a -> ((c : C) -> (R c -> Set))
      -> (a -> Set) -> Set
[[ Pure x ]] alg P = P x
[[ Op c k ]] alg P = alg c (λ x -> [[ k x ]] alg P)
\end{minted}

\pause
Let us look at \Agda{alg : (c : C) -> (R c -> Set) -> Set}'s type.
\end{frame}

@@

Now we can finish the definition and prove soundness unconditionally:
\begin{minted}{Agda}
match (r *) = Op iRec (Epsilon | r · (r *)) eitherToList

>>>>

In this work, we use a free monad to model effectful programs in Agda:

@@

\pause
The generic fold that computes a predicate of type \Set:
\begin{minted}{Agda}
[[_]] : Free C R a -> ((c : C) -> (R c -> Set) -> Set)
      -> (a -> Set) -> Set
[[ Pure x ]] alg P = P x
[[ Op c k ]] alg P = alg c (λ x -> [[ k x ]] alg P)
\end{minted}
\end{frame}

@@

Now we can finish the definition and prove soundness unconditionally:
\begin{minted}{Agda}
match (r *) = Op iRec (Epsilon | r · (r *))
